---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)

# Reading the CSV file
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQCD8cHNzQP5URY_ltg5l-_vEcGwWWwlBTdfznm2pR0Vt3d3SgaEbSEUUrWkxQ8rgg4kVjG7LDMEEsx/pub?gid=846026211&single=true&output=csv")

# Renaming columns
latest_data <- logged_data %>%
  rename(
    timestamp = 1,
    platform = 2,
    product_type = 3,
    ads_last_10_min = 4,
    ad_repeats_today = 5,
    interaction = 6,
    ad_format = 7
  )

# Summary values 
max_ads_shown <- max(latest_data$ads_last_10_min, na.rm = TRUE)
min_ads_shown <- min(latest_data$ads_last_10_min, na.rm = TRUE)
```

```{css}
img {
  display: block;
  margin-left: auto;
  margin-right: auto;
}

body{
  margin-left: 25%;
  margin-right: 25%;
}
```

## Summary of Ads Shown 
During the 10 minute of scrolling, the highest number of ads displayed was **`r max_ads_shown`**, while **`r min_ads_shown`** was the lowest.

## Ads by Platform and Format
The chart below shows how ads are distributed across different platforms, categorized by their ad format.

```{r}
ggplot(data = latest_data) +
  geom_bar(aes(x = platform, fill = ad_format)) +
  labs(
    title = "Ads On Different Platforms Categorised by Format",
    subtitle = "Comparing ads across different platform by their ad format",
    x = "Platform ad was seen",
    y = "Number of ads"
  )
```


## Ads by Product Type and Platform
The chart below shows how different type of service/product is advertised across different platforms.

```{r}
ggplot(data = latest_data) +
  geom_bar(aes(y = product_type, fill = platform)) +
  labs(
    title = "Service/Product Ad Across Differnt Platforms",
    subtitle = "Comparing ads type of service/product across different platforms",
    x = "Number of ads",
    y = "Types of service/product"
  )
```
